Further Evidence of Modified Spin-down in Sun-like Stars:\\Pile-ups in the Temperature--Period Distribution

### 2022-01-10 src/ms.tex
Removing Barnes & Kim 2010 tau_c tables

\newcommand{\taucz}{$\tau_\mathrm{cz}$\xspace}
\newcommand{\rocrit}{$\mathrm{Ro_{crit}}$\xspace}
\newcommand{\rocritfinal}{$\mathrm{Ro_{crit}}~\lesssim~2$\xspace}
\newcommand{\lamostkep}{LAMOST--Kepler\xspace}
\newcommand{\lamostmcq}{LAMOST--McQuillan\xspace}
\newcommand{\teffmin}{5800~K\xspace}
\newcommand{\agerange}{$\sim$2--6~Gyr\xspace}
\newcommand{\agemin}{$\sim$2--3~Gyr\xspace}

@@

\newcommand{\rhk}{$R'_\mathrm{HK}$\xspace}
\newcommand{\shk}{$S_\mathrm{HK}$\xspace}
\newcommand{\caiihk}{Ca II H\&K \xspace}

@@

It it also possible that the long-period pile-up studied here only applies to stars with masses $\gtrsim$~1~\msun, in which case the Sun's period and age require no explanation. However, in this scenario we would have no explanation for why hotter stars pile-up while cooler stars do not, especially given that the pile-up appears to occur at low enough Ro that the cooler stars should appear to pile up as well. As seen in Figure~\ref{fig:asteroseismic}, it is not clear that a pile-up exists for \teff~$\lesssim$~5800~K, particularly when examining the CKS and \citet{Hall2021} samples (see also \S\ref{subsec:extent}). However, kernel density estimation of the joint \teff--\prot distribution in the \lamostmcq sample, as well as a cross-match between LAMOST and \citet{Santos2021}, suggests the pile-up may exist at \teff as low as 5500~K or even 5000~K. We thus consider the explanation that WMB only operates for $\gtrsim$~1~\msun stars unlikely, and suggest that further work with a larger sample size could reveal the true \teff range of the pile-up more clearly.

>>>>

\newcommand{\taucz}{$\tau_\mathrm{cz}$\xspace}
\newcommand{\rocrit}{$\mathrm{Ro_{crit}}$\xspace}
\newcommand{\rocritfinal}{$\mathrm{Ro_{crit}}~\lesssim~2$\xspace}
\newcommand{\lamostkep}{LAMOST--Kepler\xspace}
\newcommand{\lamostmcq}{LAMOST--McQuillan\xspace}
\newcommand{\teffmin}{5500~K\xspace}
\newcommand{\agerange}{$\sim$2--6~Gyr\xspace}
\newcommand{\agemin}{$\sim$2--3~Gyr\xspace}

@@

% \newcommand{\rhk}{$R'_\mathrm{HK}$\xspace}
% \newcommand{\shk}{$S_\mathrm{HK}$\xspace}
% \newcommand{\caiihk}{Ca II H\&K \xspace}

@@

\textbf{Needs revision} It it also possible that the long-period pile-up studied here only applies to stars with masses $\gtrsim$~1~\msun, in which case the Sun's period and age require no explanation. However, in this scenario we would have no explanation for why hotter stars pile-up while cooler stars do not, especially given that the pile-up appears to occur at low enough Ro that the cooler stars should appear to pile up as well. As seen in Figure~\ref{fig:asteroseismic}, it is not clear that a pile-up exists for \teff~$\lesssim$~5800~K, particularly when examining the CKS and \citet{Hall2021} samples (see also \S\ref{subsec:extent}). However, kernel density estimation of the joint \teff--\prot distribution in the \lamostmcq sample, as well as a cross-match between LAMOST and \citet{Santos2021}, suggests the pile-up may exist at \teff as low as 5500~K or even 5000~K. We thus consider the explanation that WMB only operates for $\gtrsim$~1~\msun stars unlikely, and suggest that further work with a larger sample size could reveal the true \teff range of the pile-up more clearly.
